Merging in R

### 2021-10-02 text/05/MergingInR.Rmd
Redefined footer

You can find an [earlier version](http://www.pmean.com/05/MergingInR.html) of this page on my [original website](http://www.pmean.com/original_site.html).

>>>>

You can find an [earlier version][sim1] of this page on my [original website][sim2].

[sim1]: http://www.pmean.com/05/MergingInR.html
[sim2]: http://www.pmean.com/original_site.html
